---
title: "Verification Of Charges by courier company"
author: "Avinash Patankar"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

* #####  Steps followed to verify if the charges levied by courier company per Order are correct - 
   + step 1 :- loading the required packages
```{r libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(dplyr)
library(stringr)
library(data.table)
library(writexl)
library(splitstackshape)
library(data.table)
```
   + step 2 :- importing the required files in Rstudio
```{r}
companyx_order_report <- read_xlsx("C:\\Users\\patankar.avinash\\Downloads\\Cointab\\Company X - Order Report.xlsx")

companyx_courier_zone <- read_xlsx("C:\\Users\\patankar.avinash\\Downloads\\Cointab\\Company X - Pincode Zones.xlsx")
companyx_sku_master <- read_xlsx("C:\\Users\\patankar.avinash\\Downloads\\Cointab\\Company X - SKU Master.xlsx")
courier_company_invoice <- read_xlsx("C:\\Users\\patankar.avinash\\Downloads\\Cointab\\Courier Company - Invoice.xlsx")
courier_company_rate <- read_xlsx("C:\\Users\\patankar.avinash\\Downloads\\Cointab\\Courier Company - Rates.xlsx")

```
  + step 3 :- merging companyx_order_report and companyx_sku_master
       
      *Note :- the new files are named as D1, D2, D3.... evry time there is a major change.

        
```{r}
# deleting duplicate from companyx_sku_master
companyx_sku_master1 <- companyx_sku_master %>% distinct() 
# merging both dataframes
D1 <- merge(companyx_order_report,companyx_sku_master1,by="SKU")
```
  + step 4 :- calculating the total weight (Kg.)
```{r}
# typecasting the quantity column fron character to integer
D1$`Order Qty`<- as.numeric(as.character(D1$`Order Qty`))
D1 <- D1 %>% mutate(total_weight=`Order Qty`*`Weight (g)`/1000)
```
             
  + step  5 :- calculating total of each order
```{r}
D2 <-D1 %>% group_by(ExternOrderNo) %>% summarise(total_weight_by_order=sum(total_weight))
```
  
  + step 6 :- merging the latest D2 file with courier_company_invoice
```{r}
D3 <- merge(D2,courier_company_invoice,by.x = "ExternOrderNo",by.y="Order ID")
```
  + step 7 :- calculating weight slab 
```{r}
D3 <- D3 %>%  mutate(weight_slabs=ceiling(D3$total_weight_by_order*2)/2)
# converting charged Weight from character to double
D3$`Charged Weight`<- as.double(as.character(D3$`Charged Weight`))
D3 <- D3 %>% mutate(weight_slabs_courier_company=ceiling(D3$`Charged Weight`*2)/2)
```
  + step 8 :- merging latest D3 with companyx_courier_zone
```{r}
#deleting duplicates 
companyx_courier_zone <- distinct(companyx_courier_zone)
#typecasting pincode column
companyx_courier_zone$`Customer Pincode`<- as.character(as.integer(companyx_courier_zone$`Customer Pincode`))
# changing column name of zone to zone_x for distinguish
colnames(companyx_courier_zone)[3]="zone_x"
#merging 
D4 <- D3 %>% left_join(companyx_courier_zone,by="Customer Pincode")
```
  + step 9 :- modifying courier_company_rate
```{r warning=FALSE}
z1 <- colnames(courier_company_rate)
courier_company_rate <-  courier_company_rate %>% pivot_longer(c(z1),names_to = "zone_and_type_pay",values_to = "charges")
courier_company_rate <- cSplit(courier_company_rate,"zone_and_type_pay","_")
courier_company_rate <- courier_company_rate %>% mutate(across(zone_and_type_pay_1,str_replace,'fwd',"Forward charges")) 
courier_company_rate <- courier_company_rate %>% mutate(across(zone_and_type_pay_1,str_replace,'rto',"RTO charges"))
courier_company_rate <- courier_company_rate %>% pivot_wider(names_from = zone_and_type_pay_3,values_from  = charges)
a <- courier_company_rate %>% group_by(zone_and_type_pay_2) %>% summarise("fixed"=sum(fixed),"additional"=sum(additional))
FandRTO <- data.frame(append(a,c("zone_and_type_pay_1"="Forward and RTO charges"),after = 0))
courier_company_rate <- rbind(courier_company_rate,FandRTO)
courier_company_rate<-courier_company_rate %>% mutate("fixed + additional"=fixed+additional)

```
  + step 10 :- merging _courier_company_rate with D4
```{r}
colnames(courier_company_rate)[1]="Type of Shipment"
 colnames(courier_company_rate)[2]="zone_x"
 D5 <- D4 %>% left_join(courier_company_rate,by=c("Type of Shipment","zone_x"))
```
  + step 11 :- calculating expected charges 
```{r}
 D6 <-cbind(D5,Expected_charge=NA)
 for (i in 1:nrow(D6)) {
   x <-D6[i,10]
   if(x==0.5){
     D6[i,17]<-D6[i,14]
   }
   if(x>0.5){
     D6[i,17]<- D6[i,16]*x
   }
 }
```
  + step 12 :- finding difference between expected and billed charges
```{r}
 D6$`Billing Amount (Rs.)`<- as.double(as.character(D6$`Billing Amount (Rs.)`))
 colnames(D6)[9]="bill_amount"
 D7 <- D6 %>%  mutate("difference"=Expected_charge-bill_amount)
 D7$difference <- round(D7$difference,digits = 3)
```
  + step 13 :- getting the required table from latest dataframe D7
```{r}
 D8 <- D7[,-c(5,6,8,12,14,15,16)]
 D9 <- D8[,c(1,3,2,7,4,8,9,5,10,6,11)]
 c1 <- colnames(D9)
 setnames(D9, old = c1,new = c("Order ID","AWB Number",
                               "Total weight as per X (KG)",
                               "Weight slab as per X (KG)",
                               "Total weight as per Courier Company (KG)",
                               "Weight slab charged by Courier Company (KG)",
                               "Delivery Zone as per X",
                               "Delivery Zone charged by Courier Company",
                               "Expected Charge as per X (Rs.)",
                               "Charges Billed by Courier Company (Rs.)",
                               "Difference Between Expected Charges and Billed Charges (Rs.)"))
```
  + step 14 :- getting the output data 2 table
```{r}
a <- nrow(D9)
b<- sum(D9$`Charges Billed by Courier Company (Rs.)`)
c <- sum(D9$`Expected Charge as per X (Rs.)`)
C1 <- c("Total orders where X has been correctly charged",
        "Total Orders where X has been overcharged",
        "Total Orders where X has been undercharged",
        "Total invoice amount by courier company",
        "expected Total amount by X")
C2 <- c(0,0,0,a,a)
C3 <- c(0,0,0,b,c)
Answers <- data.frame(C1,C2,C3)
L <-0
M<-0
N<-0

for (i in 1:nrow(D9)) {
  x<- D9[i,11]
  if(x <0){ L=L+1
   Answers[2,2]<- L
     
      Answers[2,3]<-Answers[2,3]+ x*(-1)
   
  }
  if(x>=0 && x <0.5){
    M=M+1
    Answers[1,2]<-M
    Answers[1,3]<-Answers[1,3]+D9[i,9]
    
  }
  if(x >=0.5){ N=N+1
  Answers[3,2]<- N
  
  Answers[3,3]<-Answers[3,3]+x
  
  }
}
```
 + step 15 :- extracting required file
```{r}
write_xlsx(D9,"C:\\Users\\patankar.avinash\\Downloads\\Cointab\\output_data\\output_data-1.xlsx")
write_xlsx(Answers,"C:\\Users\\patankar.avinash\\Downloads\\Cointab\\output_data\\output_data-2.xlsx")
```
 
      
   
   
 
